Likelihoods for a general class of ARGs under the SMC

### 2025-02-20 paper.tex

\linenumbers
\title{Computing likelihoods under the SMC for a general class of ARGs.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/likelihood_surface}
    \caption{Log likelihood-ratio curves for ARGs containing
     varying degrees of information about the realised simulation.
    The ``Full ARG'' here is the result of an 
    \texttt{msprime} simulation of the SMC (100 diploid samples, genome length 1Mb, 
    $r=2.5\times10^{-8}$, $N_e=1\times10^4$) which contains complete 
    information about the simulated events.
    with various degrees of completeness. The likelihood ratio is computed with
    respect to the true recombination rate. 
    \label{fig:lik-surface}}
\end{figure}

>>>>

\linenumbers
\title{Likelihoods for a general class of ARGs under the SMC}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/likelihood_surface}
    \caption{Log likelihood-ratio curves for ARGs containing
     varying degrees of information about the realised simulation.
    The ``Full ARG'' here is the result of an 
    \texttt{msprime} simulation of the SMC (100 diploid samples, genome length 1Mb, 
    $r=2.5\times10^{-8}$, $N_e=1\times10^4$) which contains complete 
    information about the simulated events 
    (9,378 nodes; 13,221 edges; 2,933 trees). 
    The ``RE nodes removed'' ARG is the 
    result of simplifying out all of the recombination nodes (3,332 nodes;
    6,901 edges; note that \texttt{msprime} uses distinct nodes for the 
    left and right parent of each recombination). The ``Fully simplified''
    ARG has all locally unary nodes removed from trees (3,332 nodes; 10,674
    edges). Each of these ARGs additionally has 5\% and 25\% of the 
    internal nodes removed to create polytomies.
    See the text for details on how the likelihood ratio values are computed.
    The ``Full ARG'' and ``RE nodes deleted'' lines coincide.
    \label{fig:lik-surface}}
\end{figure}
